Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-06 paper/galsize_paper.tex
Finished draft of section 5.1

Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since trends dramatically weaken and change sign. However, even very simple models based entirely on central vs. satellite size differences can give rise to this behavior.

{\color{blue} APH: finish discussion of color and morphology.}

>>>>

Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since the trends substantially weaken and change sign. However, even very simple models based entirely on central vs. satellite size differences can give rise to this behavior. For example, it is well known that satellites are redder than centrals \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much stronger relative to blue \citep{zehavi_etal11}. Pre-selecting galaxy samples by color will thus significantly weaken the dynamic range of $F_{\rm sat}$ within each color-selected subsample. This reduction in the role of satellites could be sufficient for the $\rhalf\propto\rvir\propto\mhalo$ of {\em central} galaxies to become the dominant effect, which would result in the mild, reversed trend seen in the top panels of Figure \ref{fig:colorclustering}. The same mechanism could be at work for the case of morphology pre-selection, except that for disk-dominated systems, there would need to be a larger residual correlation with satellite designation relative to blue-selected samples \citep[This is, in fact, exactly the trend reported in][]{weinmann_etal08}.

While we consider such an explanation plausible, a conclusive determination of the principles underlying the clustering trends shown in Figure \ref{fig:colorclustering} requires proper forward modeling of morphology and color jointly with galaxy size. Such an effort is beyond the scope, but well-motivated, by the present work.
